\chapter{Product environment}

\paragraph{Providing ROOT to Node.js}
As mentioned previously in \hyperlink{section.2.1}{section 2.1} with Node.js bindings for ROOT writing ROOT applications based on the client-server model becomes simplified and offers solutions based on state of the art web technologies especially through the applied concept of separation of data processing and data visualization.

\section{Software}
\subsection{ROOT}
ROOT is a software framework for data analysis and I/O. It may be used to process and especially visualize big amounts of scientific data, e.g. the petabytes of data recorded by the Large Hadron Collider experiments every year.\\
Since the framework comes with an interpreter for the C++ programming language, for rapid and efficient prototyping and a persistency mechanism for C++ objects, ROOT based applications are  extensible and as feature rich as the C++ language itself.
A detailed introduction to the ROOT framework may be found in the \textit{ROOT  primer}\footnote[1]{\url{https://root.cern.ch/root/html534/guides/primer/ROOTPrimer.html}}
on the CERN website.\\
Interfacing with ROOT is done dynamically, since ROOT shares all the necessary information on its (global) functions during runtime.

\subsection{Node.js}
Node.js is an open-source, cross-platform runtime environment for developing server-side web applications. Node.js applications are written in JavaScript and may act as a stand-alone web server. It uses Google V8 JavaScript engine to execute code.\\
The Binding API to be developed will be a so called native Node.js module written in C++. It interfaces directly with the V8 API to provide (non-blocking) encapsulation of ROOT objects as Javascript equivalents.

\section{Hardware}
Since the Bindings, in simplified terms, just provide data structures for encapsulation of ROOT object or rather functions, the hardware requirements of the bindings themselves should be negligible.\\
Basically calling a ROOT function via the Binding-API inside a Node.js application really should not take up a huge amount of additional resources compared to a direct function call inside a native ROOT application.
In conclusion there are no additional hardware requirements for using the Bindings on a computer that was able to run native ROOT applications before - this includes almost any modern Desktop PC.
